Hybrid platforms and bargaining power

### 2023-02-03 src/paper/application.tex
Add some lemmas

\section{Model}
\label{sec:model}

@@

Proposition \ref{prop:one_sided} gives a simple formula for the Shapley value of the platform in case $N_F$ fringe firms made the initial investment:
\begin{align*}
    \pi^t_P &= \varphi_P = \int_0^1 v(tN_F) \dt \\
            &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right]
\end{align*}
Subsequently, the fringe gets the remainder of the profits, therefore
\begin{align*}
    \pi^v_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
            &= \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
\end{align*}
and the total profits of the whole fringe are
\begin{align*}
    \pi^v_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F
\end{align*}
The free entry condition implies that fringe profits are zero, therefore the number of fringe entrants is given by the implicit equation
\begin{align}
    \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F = 0
    \label{eq:free_entry_bargaining}
\end{align}

@@

>>>>

\section{Example}
\label{sec:model}

@@

Proposition \ref{prop:one_sided} gives a simple formula for the Shapley value of the platform in case $N_F$ fringe firms made the initial investment:
\begin{align*}
    \pi^t_P &= \varphi_P = \int_0^1 v(tN_F) \dt \\
            &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right]
\end{align*}
Subsequently, the fringe gets the remainder of the profits, therefore
\begin{align}
    \pi^v_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
            &= \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
            \label{eq:fringe_variable_profit}
\end{align}
and the total profits of the whole fringe are
\begin{align*}
    \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F
\end{align*}
The free entry condition implies that fringe profits are zero, therefore the number of fringe entrants is given by the implicit equation
\begin{align}
    \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F = 0
    \label{eq:free_entry_bargaining}
\end{align}

@@

\section{Miscellaneous lemmas and proofs}

The following proposition shows that, if the platform is operating in a more hybrid mode (meaning it has more or better products), then, for a given aggregate size, the fringe obtains a lower share of the profits.
This is due to the increased bargaining power of the platform.

\begin{proposition}
    \label{prop:fringe_profit_decreasing_in_N_P}
    For a fixed aggregate size $A$, fringe profit is decreasing in $N_P$ and $V_P$.
\end{proposition}
\begin{proof}
    Let $N_P' V_P' > N_P V_P$.
    Furthermore, let $N_F V_F = A - N_P V_P - 1$ and $N_F' V_F' = A - N_P' V_P' - 1$ for some $A > 1$.
    Finally, let
    \begin{align*}
        v(n) &= \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}, \\
        v'(n) &= \mu \frac{n V_F + N_P' V_P'}{n V_F + N_P' V_P' + 1}.
    \end{align*}

    Observe that for any $t \in [0, 1)$,
    \begin{align*}
        v(tN_F) &= \frac{t N_F V_F + N_P V_P}{t N_F V_F + N_P V_P + 1} \\
                &= \frac{tA - t + (1 - t) N_P V_P}{tA - t + (1 - t) N_P V_P + 1} \\
                &< \frac{tA - t + (1 - t) N_P' V_P'}{tA - t + (1 - t) N_P' V_P' + 1} \\
                &= \frac{t N_F' V_F' + N_P' V_P'}{t N_F' V_F + N_P V_P + 1} \\
                &= v'(tN_F').
    \end{align*}
    This in turn implies that
    \begin{align*}
        \pi_F^v = \int_0^1 v(t) \dt < \int_0^1 v'(t) \dt = (\pi_F^v)',
    \end{align*}
    which is what we wanted to show.

\end{proof}

\begin{lemma}
    \label{lem:shape_of_pi_F}
    For any $V_F, N_P, V_P, \mu$, the function $\pi^v_F$ is either concave in $N_F$ or decreasing in $N_F$.
\end{lemma}
\begin{proof}
    Did not manage to prove it yet.
\end{proof}

\begin{corollary}
    \label{cor:unique_eq}
    There is at most one equilibrium with $N_F > 0$.
\end{corollary}

\begin{proposition}
    \label{prop:A_decreasing_in_N_P}
    The equilibrium aggregate size $A$ is monotonically decreasing in $N_P$ and $V_P$. When the fringe is feasible to begin with, the decrease is strict.
\end{proposition}
\begin{proof}
    From proposition \ref{prop:fringe_profit_decreasing_in_N_P}, we know that the fringe profit is decreasing in $N_P$ and $V_P$.
    Furthermore, lemma \ref{lem:shape_of_pi_F}
\end{proof}

\begin{corollary}
    \label{consumer_welfare_decreasing_in_N_P}
\end{corollary}
\begin{proof}

\end{proof}
